Group Fou\\*R* Term Project Proposal

### 2018-12-13 Proposal.Rmd
.

---
title: "Group Fou*R* Term Project Proposal"
subtitle: "MEF University - BDA 503 Essentials of Data Analytics - Fall 2018"
output: html_document
---

>>>>

---
title: "Group Fou\\*R* Term Project Proposal"
subtitle: "MEF University - BDA 503 Essentials of Data Analytics - Fall 2018"
output: html_document
---
